---
title: "mypackage"
author: "Violeta&Yixuan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Package for lab 4}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This package contains the function linreg that creates a linear regression using 
ordinary least squares.
This function takes a formula and a data.frame and returns and linreg object.

```{r}
library(mypackage)
```

For example, we take the iris data.frame and the formula PetalLength~Species, 
and create our linreg object:
```{r}
lin1 <- linreg(formula = Petal.Length ~ Species, data = iris)
```

The linreg function contains differents methods implemented:

print(): we should have the printout as call of the regressions coefficients.

```{r}
lin1$print()
```

plot(): should plot the following two plots of residuals Vs fitted Values.
We need install the libraries ggplot2 and gridExtra.
```{r}
library(ggplot2)
library(gridExtra)
lin1$plot()
```

coeff(): should return the regressions coefficients
```{r}
lin1$coeff()
```

residual(): should return the vector of residuals e of the regression
```{r}
lin1$residual()
```

pred(): should return the predicted values of the regression
```{r}
lin1$pred()
```

summary(): should return a summary of the linear regression similar as the printout for lm objects. 
```{r}
lin1$summary()
```

